Efficient Coalition Formation \\ for Web Services

### 2013-06-16 papers/coalition-journal-extension/coalition_journal.tex
Changes

We discuessed $core$ as one the preminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating. The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view. It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit. However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. To this end, our communities will reward and valuate web services in the community

>>>>

We discuessed $core$ as one the preminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating. One way for communities to ensure community stability could be applying a $\epsilon$ ammount of cost for web services changing communities. However this would need all community masters to agree on and this will not work for webservices gaining more when working alone. Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community masters. These concepts of applying changes in coalition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.

The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view. It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit. Communities can agree on However, in our case, the community master is willing to keep web services in communities too. There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with. To this end, our communities will reward and valuate web services in the community
